Active Learning from Blackbox to Timed Connectors

### 2016-01-12 paper/paper.tex
.

% --------------------------------------- information -------------------------------------------
\title{Active Learning from Blackbox to Timed Connectors}
\author{
\IEEEauthorblockN{Yi Li\IEEEauthorrefmark{1} and Meng Sun\IEEEauthorrefmark{1}}
\IEEEauthorblockA{
\IEEEauthorrefmark{1}Department of Informatics, School of Mathematical Sciences, Peking University,
Beijing, China\\
liyi\_math@pku.edu.cn, summeng@math.pku.edu.cn
}
}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=.4\textwidth]{./images/activelearning.png}
  \end{center}
  \caption{Active Automata Learning}
  \label{fig:activelearning}
\end{figure}

Figure \ref{fig:activelearning} shows a sketch of active learning, wherein:
\begin{itemize}
  \item[-]
\end{itemize}

More details on the algorithm will be presented in Section \ref{sec:activelearning}.

>>>>

% --------------------------------------- information -------------------------------------------
\title{Active Learning from Blackbox to Timed Connectors}
\author{
\IEEEauthorblockN{Yi Li\IEEEauthorrefmark{1}, Yiwu Wang\IEEEauthorrefmark{1} and Meng Sun\IEEEauthorrefmark{1}}
\IEEEauthorblockA{
\IEEEauthorrefmark{1}Department of Informatics, School of Mathematical Sciences, Peking University,
Beijing, China\\
liyi\_math@pku.edu.cn, yiwuwang@126.com, summeng@math.pku.edu.cn
}
}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=.5\textwidth]{./images/activelearning.png}
  \end{center}
  \caption{Active Automata Learning}
  \label{fig:activelearning}
\end{figure}

Figure \ref{fig:activelearning} shows the sketch of active automata learning, wherein:
\begin{itemize}
  \item[-] \emph{Teacher} and \emph{Student}. Active learning is an interactive process where
    students ask questions and teachers answer. Here learning algorithm plays the role of student.
  \item[-] \emph{Oracles} is an interface specifying which kind of questions can be answered by the
    teacher.
  \item[-] \emph{SUL} is an abbreviation of System Under Learn. The name comes from a well-known
    concept SUT (System Under Test) in software testing. In this case, we use blackbox models as our
    SULs.
  \item[-] \emph{CEGAR} indicates Counter-Example Guided Abstraction
    Refinement\cite{DBLP:conf/cav/ClarkeGJLV00}. In active learning, we need counter-examples to
    guide us on further quries and cover the undistinguished states.
\end{itemize}

When applying active automata learning on some model, firstly we assume that it should be equivalent
to some \emph{Mealy machine}. In other words, a deterministic model accepting a finite set of input
symbols and mapping them to a finite set of output symbols.

Such a model is encapsulated as a \emph{teacher} by the \emph{Oracle}, which handles
all communication with the model, both providing input and obtaining output. Also, it serves as a
so-called \emph{Minimal Adequate Teacher} interface, which is responsible for two types of
queries.

\begin{itemize}
  \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) The name comes from
    some grammar-learning papers (e.g. \cite{DBLP:journals/iandc/Angluin87}), where \emph{mq} checks
    if a word is a member of certain language defined by the given grammar. When it comes to
    automata learning, \emph{mq} is supposed to provide simulation results for given input
    sequences.
    \todo{example, also a mealy-machine example}
  \item[-] \textbf{Equivalence Query} (hereinaftr referred to as \emph{eq}) Given a hypothesis
    (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
    equivalent to the system-under-learn and generates a counter-example if needed.
\end{itemize}

These queries are given by \emph{learning algorithms}, or so-called \emph{students} in Figure
\ref{fig:activelearning}. From the \emph{mq} results, a learning algorithm should construct a
\emph{hypothesis} and check it with \emph{eq}. If counter-examples are found, we turn back and
repeat the hypothesis construction until the equivalence query returns \emph{true}.

More details on the active automata learning algorithm will be presented in Section
\ref{sec:activelearning}.
